---
title: "Leaflet"
author: "The Johns Hopkins Data Science Lab"
always_allow_html: yes
editor_options: 
  markdown: 
    wrap: 72
---

# Introduction

Leaflet is one of the most popular Javascript libraries for creating
interactive maps. The leaflet R package allows you to create your own
leaflet maps without needing to know any Javascript!

### Installation

```{r}
# install.packages("raster", repos='http://r-forge.r-project.org/', type = 'source')
# install.packages("leaflet")
```

## Your First Map

Getting started with leaflet is easy. The `leaflet()` function creates a
map widget that you can store in a variable so that you can modify the
map later on. You can add features to the map using the pipe operator
(`%>%`) just like in dplyr. The `addTiles()` function adds mapping data
from [Open Street Map](http://www.openstreetmap.org/).

```{r, eval=FALSE}
library(leaflet)
my_map <- leaflet() %>% 
  addTiles()
my_map
```

# Adding Markers

You can add markers to your map one at a time using the `addMarkers()`
function by specifying the longitude and latitude.
([Here's](https://twitter.com/drob/status/719927537330040832) a tip if
you tend to mix them up.) You can specify popup text for when you click
on the marker with the `popup` argument.

```{r, eval=FALSE}
library(leaflet)
my_map <- my_map %>%
  addMarkers(lat=39.2980803, lng=-76.5898801, 
             popup="Jeff Leek's Office")
my_map
```

## Adding Many Markers

Adding one marker at a time is often not practical if you want to
display many markers. If you have a data frame with columns `lat` and
`lng` you can pipe that data frame into `leaflet()` to add all the
points at once.

```{r, echo=FALSE}
set.seed(2016-04-25)
df <- data.frame(lat = runif(20, min = 39.2, max = 39.3),
                 lng = runif(20, min = -76.6, max = -76.5))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers()
```

## Making Custom Markers

The blue markers that leaflet comes packaged with may not be enough
depending on what you're mapping. Thankfully you can make your own
markers from `.png` files.

```{r, eval=FALSE}
hopkinsIcon <- makeIcon(
  iconUrl = "https://img.icons8.com/fluency/2x/cross.png",
  iconWidth = 50, iconHeight = 50,
  iconAnchorX = 25, iconAnchorY = 25
)

hopkinsLatLong <- data.frame(
  lat = c(39.2973166, 39.3288851, 39.2906617),
  lng = c(-76.5929798, -76.6206598, -76.5469683))

hopkinsLatLong %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = hopkinsIcon)
```

## Adding Markers with Multiple Popups

When adding multiple markers to a map, you may want to add popups for
each marker. You can specify a string of plain text for each popup, or
you can provide HTML which will be rendered inside of each popup.

```{r, echo=FALSE}
hopkinsSites <- c(
  "<a href='http://www.jhsph.edu/'>East Baltimore Campus</a>",
  "<a href='https://apply.jhu.edu/visit/homewood/'>Homewood Campus</a>",
  "<a href='http://www.hopkinsmedicine.org/johns_hopkins_bayview/'>Bayview Medical Center</a>",
  "<a href='http://www.peabody.jhu.edu/'>Peabody Institute</a>",
  "<a href='http://carey.jhu.edu/'>Carey Business School</a>"
)

hopkinsLatLong %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = hopkinsIcon, popup = hopkinsSites)
```

Customizing Marker Icons You can provide custom markers in one of
several ways, depending on the scenario. For each of these ways, the
icon can be provided as either a URL or as a file path.

For the simple case of applying a single icon to a set of markers, use
`makeIcon()`

```{r}
crossIcon <- makeIcon(
  iconUrl = "https://img.icons8.com/fluency/2x/cross.png",
  iconWidth = 38, iconHeight = 95,
  iconAnchorX = -6.2, iconAnchorY = 55.3,
)

leaflet(data = Map_DF) %>% addTiles() %>%
  addMarkers(~Longitude, ~Latitude, icon = crossIcon)
```

```{r}
library(leaflet) 
mymap <- leaflet() %>% addTiles() 

mymap %>% addMarkers(data=df,df[1,"Lon"],df[1,"Lat"], icon = JS("L.icon({
    iconUrl: 'http://icons.iconarchive.com/icons/artua/star-wars/128/Master-Joda-icon.png',
    iconSize: [75, 75]
  })"))
```

```{r}
greenLeafIcon <- makeIcon(
  iconUrl = "https://leafletjs.com/SlavaUkraini/examples/custom-icons/leaf-green.png",
  iconWidth = 38, iconHeight = 95,
  iconAnchorX = 22, iconAnchorY = 94,
  shadowUrl = "https://leafletjs.com/SlavaUkraini/examples/custom-icons/leaf-shadow.png",
  shadowWidth = 50, shadowHeight = 64,
  shadowAnchorX = 4, shadowAnchorY = 62
)

leaflet(data = quakes[1:4,]) %>% addTiles() %>%
  addMarkers(~long, ~lat, icon = greenLeafIcon)
```

# Mapping Clusters

Sometimes you might have so many points on a map that it doesn't make
sense to plot every marker. In these situations leaflet allows you to
plot clusters of markers using
`addMarkers(clusterOptions = markerClusterOptions())`. When you zoom in
to each cluster, the clusters will separate until you can see the
individual markers.

```{r, eval=FALSE}
df <- data.frame(lat = runif(500, min = 39.25, max = 39.35),
                 lng = runif(500, min = -76.65, max = -76.55))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions())
```

## Mapping Circle Markers

Instead of adding markers or clusters you can easily add circle markers
using `addCircleMarkers()`.

```{r, eval=FALSE}
df <- data.frame(lat = runif(20, min = 39.25, max = 39.35),
                 lng = runif(20, min = -76.65, max = -76.55))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers()
```

## Mapping Circle Markers

```{r, echo=FALSE}
df <- data.frame(lat = runif(20, min = 39.25, max = 39.35),
                 lng = runif(20, min = -76.65, max = -76.55))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers()
```

## Drawing Circles

You can draw arbitrary shapes on the maps you create, including circles
and squares. The code below draws a map where the circle on each city is
proportional to the population of that city.

```{r, eval=FALSE}
md_cities <- data.frame(name = c("Baltimore", "Frederick", "Rockville",
                                 "Gaithersburg", "Bowie", "Hagerstown", 
                                 "Annapolis", "College Park", "Salisbury", "Laurel"
                                 ),
                        pop = c(619493, 66169, 62334, 61045, 55232,
                                39890, 38880, 30587, 30484, 25346),
                        lat = c(39.2920592, 39.4143921, 39.0840, 39.1434, 39.0068, 39.6418, 38.9784, 38.9897, 38.3607, 39.0993),
                        lng = c(-76.6077852, -77.4204875, -77.1528, -77.2014, -76.7791, -77.7200, -76.4922, -76.9378, -75.5994, -76.8483))
md_cities %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(weight = 1, radius = sqrt(md_cities$pop) * 30)
```

```{r, echo=FALSE}
md_cities <- data.frame(name = c("Baltimore", "Frederick", "Rockville", "Gaithersburg", 
                                 "Bowie", "Hagerstown", "Annapolis", "College Park", "Salisbury", "Laurel"),
                        pop = c(619493, 66169, 62334, 61045, 55232,
                                39890, 38880, 30587, 30484, 25346),
                        lat = c(39.2920592, 39.4143921, 39.0840, 39.1434, 39.0068, 39.6418, 38.9784, 38.9897, 38.3607, 39.0993),
                        lng = c(-76.6077852, -77.4204875, -77.1528, -77.2014, -76.7791, -77.7200, -76.4922, -76.9378, -75.5994, -76.8483))
md_cities %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(weight = 1, radius = sqrt(md_cities$pop) * 30)
```

## Drawing Rectangles

You can add rectangles on leaflet maps as well:

```{r, eval=FALSE}
leaflet() %>%
  addTiles() %>%
  addRectangles(lat1 = 37.3858, lng1 = -122.0595, 
                lat2 = 37.3890, lng2 = -122.0625)
```

```{r, echo=FALSE}
leaflet() %>%
  addTiles() %>%
  # two opposite corners of rectangle
  addRectangles(lat1 = 37.3858, lng1 = -122.0595, 
                lat2 = 37.3890, lng2 = -122.0625)
```

# Adding Legends

Adding a legend can be useful if you have markers on your map with
different colors:

```{r, eval=FALSE}
df <- data.frame(lat = runif(20, min = 39.25, max = 39.35),
                 lng = runif(20, min = -76.65, max = -76.55),
                 col = sample(c("red", "blue", "green"), 20, replace = TRUE),
                 stringsAsFactors = FALSE)

df %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(color = df$col) %>%
  addLegend(labels = LETTERS[1:3], colors = c("blue", "red", "green"))
```

```{r, echo=FALSE, message=FALSE}
df <- data.frame(lat = runif(20, min = 39.25, max = 39.35),
                 lng = runif(20, min = -76.65, max = -76.55),
                 col = sample(c("red", "blue", "green"), 20, replace = TRUE),
                 stringsAsFactors = FALSE)

df %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(color = df$col) %>%
  addLegend(labels = LETTERS[1:3], colors = c("blue", "red", "green"))
```

# Conclusion

For more details about the leaflet package for R visit
<http://rstudio.github.io/leaflet/>.
