---
title: "Plotly Assignment"
author: "Jim Coen"
data: "`r format(Sys.Date(), '%A, %B %d, %Y') `"
output:
  ioslides_presentation:
    logo: ../images/corporate-finance-inst.jpeg
  beamer_presentation: default
  slidy_presentation: default
always_allow_html: yes
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(data.table)
library(ggplot2)
library(magrittr)
library(plotly)
```


<style>
div.footnotes {
  position: absolute;
  bottom: 0;
  margin-bottom: 10px;
  width: 80%;
  font-size: 0.6em;
}
</style>

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>
<script>
$(document).ready(function() {
  $('slide:not(.backdrop):not(.title-slide)').append('<div class=\"footnotes\">');

  $('footnote').each(function(index) {
    var text  = $(this).html();
    var fnNum = (index+1).toString();
    $(this).html(fnNum.sup());

    var footnote   = fnNum + '. ' + text + '<br/>';
    var oldContent = $(this).parents('slide').children('div.footnotes').html();
    var newContent = oldContent + footnote;
    $(this).parents('slide').children('div.footnotes').html(newContent);
  });
});
</script>


```{r}
library(readr)

temp_data <- read_csv("../data/LoehleEandE2007.csv", 
                      col_names = c("Date", "dev_deg_C"), 
                      skip = 2)
setnames(temp_data, "Date", "Year")
```


```{r}
library(readxl)

##excel_sheets("../data/law2006.xls")
rare_gas_data <- read_excel("../data/law2006.xls", 
                       sheet = "SplineFit20yr",
                       skip = 3 )
# select CO2 data
co2_data <- rare_gas_data[, c(5, 6)]
setnames(co2_data,  "Year AD...5", "Year")
setnames(co2_data,  "CO2 Spline (ppm)", "CO2")
rm("rare_gas_data")
```

## Climate Realism

```{r}
fig1 <- plot_ly(temp_data, 
                x = ~Year, y = ~dev_deg_C, 
                type = 'scatter', 
                mode = 'lines',
                line = list(color = 'rgb(205, 12, 24)', width = 2),
                name = "Temp") 
fig2 <- plot_ly(co2_data, 
                x = ~Year, y = ~CO2, 
                type = 'scatter', mode = 'lines',
                line = list(color = 'rgb(22, 96, 167)', width = 2),
                name = "CO2") 

fig <- subplot(fig1, fig2, nrows = 2, shareX = TRUE) %>% 
  layout(title = list(text = "Temperature and CO2"),
         plot_bgcolor='#e5ecf6', 
         xaxis = list( 
           zerolinecolor = '#ffff', 
           zerolinewidth = 2, 
           gridcolor = 'ffff'), 
         yaxis = list( 
           zerolinecolor = '#ffff', 
           zerolinewidth = 2, 
           gridcolor = 'ffff')) 
ggplotly(fig, dynamicTicks = TRUE) %>%
  rangeslider() 

```
Temperature is deviation from the average and CO2 is in ppm.<footnote>Move the range slider in the bottom plot to focus on specific years</footnote>

## Source Data:

[Historical CO2 records from Law Dome ice cores](https://view.officeapps.live.com/op/view.aspx?src=https%3A%2F%2Fwww.ncei.noaa.gov%2Fpub%2Fdata%2Fpaleo%2Ficecore%2Fantarctica%2Flaw%2Flaw2006.xls&wdOrigin=BROWSELINK)

Loehle, C. (2007) ‘A 2000-Year Global Temperature Reconstruction Based on Non-Tree ring Proxies’, Energy & Environment, 18(7), pp. 1049–1058. doi: 10.1260/095830507782616797.

[Temperature](https://www.ncasi.org/?s=2000+year+global+temperature+non-tree+ring+loehle)
